Verifying Demonstrations

### 2018-08-20 paper/security-properties.tex
Updates system, adversary model section
Cleans up a bit in security-properties section

\subsection{Security requirements}%
\label{Properties}

%\subsubsection{An overview of the adversary}

@@

\sonja{discussion about applicable properties here, more sources and alternative properties}
\sonja{new}
Difference to e-voting:
physical presence means support for a cause if there is one protest. If there is a counterprotest, physical presence with that group means support for the counterprotest. In our system, it gets more ambiguous as the participants are counted if all of the following is true 1) they participate in the protocol, 2) they use the protest identifier (cause) for which the count is done, 2) they meet the eligibility criteria, and 3) they receive enough proof shares, 4) that are uploaded to the ledger. Thus one could participate in a protest and be counted even when physically present at a counter-protest if the two protests are co-located and the participant chooses the corresponding cause/identifier of the original protest.

@@

The privacy properties we need in this context are

involuntary participant unlinkability: unless the participant discloses the receipt (by revealing her identity), there is no link between the protest data on the ledger and the identity of the participant.

involuntary witness unlinkability: unless the witness discloses the receipt (by revealing her identity), there is no link between the protest data on the ledger and the identity of the witness.
\sonja{old}
In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).

>>>>

\subsection{Security requirements}%
\label{security-properties}

@@

\sonja{discussion about applicable properties here, more sources and alternative properties}
\sonja{new}
Difference to e-voting:
physical presence means support for a cause if there is one protest. If there is a counterprotest, physical presence with that group means support for the counterprotest. In our system, it gets more ambiguous as the participants are counted if all of the following is true
\begin{enumerate*}
\item they participate in the protocol,
\item they use the protest identifier (cause) for which the count is done,
\item they meet the eligibility criteria, and
\item they receive enough proof shares,
\item that are uploaded to the ledger.
\end{enumerate*}
Thus one could participate in a protest and be counted even when physically 
present at a counter-protest if the two protests are co-located and the 
participant chooses the corresponding cause/identifier of the original protest.

@@

The privacy properties we need in this context are
\begin{description}
  \item[involuntary participant unlinkability] unless the participant discloses 
    the receipt (by revealing her identity), there is no link between the 
    protest data on the ledger and the identity of the participant.

  \item[involuntary witness unlinkability] unless the witness discloses the 
    receipt (by revealing her identity), there is no link between the protest 
    data on the ledger and the identity of the witness.
\end{description}
\sonja{old}
In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).
